Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
revise abstract

This paper introduces a generic hierarchical modeling of acoustic scenes using features computed using the time scattering transform  for time spans below the second and object-based segmentation for larger time spans that effectively model the scene.

Application of the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets and state-of-the-art classifier demonstrates its potential. More precisely, features derived from the time scattering transform consistently outperform Mel-frequency cepstral coefficients (MFCCs) for both tasks.

Representing the scene at larger time scale as a set of examplars of coherent segments is an effective approach for similarity retrieval as it allows the retrieval system to focus on discriminative features. This benefit is reduced in supervised settings, probably because the much of the discriminability potential of the approach is already learned by the classifier.

>>>>

This paper introduces a generic hierarchical modeling of acoustic scenes using the wavelet scattering features for time spans below the second and object-based segmentation for larger time spans that effectively model the scene.

Application of the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets and state-of-the-art classifier demonstrates its potential. More precisely, features derived from the scattering transform consistently outperform Mel-frequency cepstral coefficients (MFCC) for both tasks.

Representing the scene at larger time scale as a set of examplars of coherent segments is an effective approach for similarity retrieval as it allows the retrieval system to focus on discriminative features. This benefit is reduced in supervised settings, probably because much of the discriminability potential of the approach is already learned by the classifier.
